Baseline centering problem

### 2018-11-30 paper/tangotd.tex

Combined with all this, is the problem that a Bellman solution on the
support of $\rho$ may be very, very far from the global Bellman solution,
even on the support of $\rho$ (take random walk on a circle, with $\rho$
being everything but one point: then any linear function solves Bellman
on the support of $\rho$).

The minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, the $\rho^2$ is a bit weird... moreover having
$\transp{\Delta}\Delta$ means we are just facing the double sampling
problem (we can sample $\transp{(\rho\Delta)}\rho\Delta$, but in practice the sample will always be $0$
unless we are lucky and select two transitions $s\to s'$ that have the
same $s$). Even the right-hand-side involves double sampling.

The minimizer of a weird norm $L^2(\rho \Phi\transp{\Phi}\rho)$ is better
samplable, because now it's enough to sample states \emph{with the same
features}, not just the exact same state. This is basically what happens
in the linear case. The features should not be orthogonal. Should use a
hash of states instead? Or apply ReLU to orthogonal features.

@@

>>>>

The minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, having
$\transp{\Delta}\rho^2\Delta$ means we are just facing the double sampling
problem (we can sample $\transp{(\rho\Delta)}\rho\Delta$, but in practice the sample will always be $0$
unless we are lucky and select two transitions $s\to s'$ that have the
same $s$). Even the right-hand-side involves double sampling.

If one has access to some features $\Psi$,
the minimizer of a weird norm $L^2(\rho \Psi\transp{\Psi}\rho)$ is better
samplable, because now in double sampling it's enough to sample states \emph{which share
some
features}, not just the exact same state. This is basically what happens
in the linear case, with $\Psi=\Phi$. In the nonlinear case taking
$\Psi=\Phi$ is not acceptable because $\Phi$ depends on $\theta$, so the
objective is not a fixed norm to be minimized. The features $\Psi$ should not be orthogonal. Should use a
hash of states instead? Or apply ReLU to orthogonal features.

@@

[Combined with all these problems, is the problem that a Bellman solution on the
support of $\rho$ may be very, very far from the global Bellman solution,
even on the support of $\rho$ (take random walk on a circle, with $\rho$
being everything but one point: then any linear function solves Bellman
on the support of $\rho$).]
